\chapter{Introduction}


\section{Motivation}

Supply demand imbalance, natural calamities etc. may not always be the reason behind the rise in the price of a commodity. ​It may be a consequence of artificial supply deficit planned intelligently by traders’ nexus for profiteering through manipulation of supply of commodity and hence indirectly controlling their prices. ​Our attempt is to locate such hikes in prices which seem suspicious (we call them anomalies).​ To detect and analyse the characteristics of anomalies in the prices of commodities. Currently we have considered the case of onion and based on that we are looking forward to develop library for any time-series.


\section{Objective}

Our objective is that we need to highlight anomalies which may be an indicator of illegal market manipulation act by traders nexus in the provided time series.For this purpose we need to create library with some set of functionalities to detect anomalies in the give input time series. Anomalies will be based on the hypothesis stated by the user. For particular scenario stated by user, execute appropriate algorithms and report the anomalies in the time series.


\section{Relavence of Project}

Anomaly detection techniques help to explore situations which might be different from the expected behavior and could reveal interesting facts. It is used many areas which are explained in detail in next chapter. The project aims to raise potential red flags for days which are suspect of illicit market manipulation activities by set of traders. This type of monitoring system may help people monitor and hence control these illicit market manipulations better.
For example, unnecessary hike in the prices may be due to wrong government policies, loopholes in the supply chain of commodity, intention of profiteering by traders etc. So our project will help journalist or end user interested in detecting such abnormal behavior.
